Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-07 paper/main.tex
Added Unit Test descriptions

\subsection{Unit tests}
% TODO: Include the use of Known Answer Tests

>>>>

\subsection{Unit tests}
We Unit Test each new candidate implementation that is included SHA3lib, both
to verify our own work and to verify that the implementation from \ac{SUPERCOP}
actually are correct.

\paragraph{Known-Answer Tests} are used to check that the implementation conform
to the specifications of the algorithm author. The \ac{KAT}s include
bytestrings, their length and their expected message digest. The length of the
inputs range from 0 bits to 34304 bits, and also include a message that should
be repeated for about 17 million times, to verify that the implementation can handle
large inputs.

\paragraph{Basic Hash Tests} is what we have named the set of tests which test
the core basics of what a hash function implementation will have to be able to
do to be usable. This include that Init(), Update() and Final() works as
expected, and that the output is of correct size. This include that every
function should produce the same digest for the inputs Update("foofoo") and two
consecutive calls to Update("foo").

\paragraph{Copy Hash Tests} does not test any of the functionality used by
Tahoe, but the copy()-function is a part of Hashlib. The idea is that if we
have two bytestring that share a common prefix, we can input this prefix to
Update(), then copy the state. The tests check if this is possible, and that a
copy of the state and following update does not affect the original state.
